---
title: "Analysis of Indian States and cities"
author: "Abhinesh"
date: "07 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
```
```{r  echo=FALSE, message=FALSE, warning=FALSE}
india=read.csv("CSV/cities_r2.csv");
library(leaflet)
library(dplyr)
mapIndia <- leaflet() %>% 
  addTiles('http://{s}.basemaps.cartocdn.com/dark_all/{z}/{x}/{y}.png',
           attribution='Map by  AKGARHWAL') %>%
  setView(80, 25, zoom= 4)

mapObj = mapIndia %>% addCircles (data=india, lat= india$latitude, lng  = india$longitude, 
                 popup=paste(
  "<strong>City : </strong>", india$name_of_city,
  "<br><strong>State : </strong>", india$state_name,
  "<br><strong>Total Population : </strong>", india$population_total,
  "<br><strong>Child Population : </strong>", india$X0.6_population_total,
  "<br><strong>Literacy Rate : </strong>", india$effective_literacy_rate_total,
  "<br><strong>Total Literate : </strong>", india$total_graduates,
   "<br><strong>Sex ratio : </strong>", india$sex_ratio),
                            
  weight = ifelse(india$population_total < 500000, 3,ifelse(india$population_total < 1000000, 7,ifelse(india$population_total >= 1000000, 12,20))), 
   color= ifelse(india$population_total < 500000, "dodgerblue",ifelse(india$population_total < 1000000, "lawngreen",ifelse(india$population_total >= 1000000, "red","#FF0000"))), 
   stroke = TRUE, fillOpacity = 0.6)
```
```{r}
#Diaplay Map of India with top 500 City
mapObj
```

## 1. Population Analysis
**1.A** Rural and Urban Population Comparison
```{r echo=FALSE}
#Read from File
fileObj = read.csv("CSV/State_Population.csv")
#Now draw graph using highcharter library

```
```{r echo=FALSE}
states = fileObj$State
population = fileObj$Population
#Convert to Data frame
data = data.frame(states,population)
#Draw Graph
```
```{r}
hchart(data,"bar",hcaes(x=states,y = population),name="population",colorByPoint = TRUE) %>% hc_title(text = "State by Total Population.")
```
```{r}
Graph <- highchart() %>% 
  hc_xAxis(categories = fileObj$State ) %>% 
  hc_add_series(name = "Total Population", data = fileObj$Population ) %>% 
  hc_add_series(name = "Rural Population", data = fileObj$Rural.Population) %>% 
  hc_add_series(name = "Urban Population", data = fileObj$Urban.Population) %>% 
  hc_title(text="Comparision of Population of States") 
Graph
```



**Analysis**<br>
From above graph we conclude that <br>
(1)State With maximum population : Uttar Pradesh<br>
State with minimum population : Sikkim<br>

(2)Sate with maximum  rural population : Uttar Pradesh<br>
Sate with minimum  rural population : Sikkim<br>

(3)Sate with maximum  urban population : Maharashtra<br>
Sate with minimum  urban population : Sikkim<br>

(4)Sikkim has least population in each 
category.<br>

(5)State with less rural populatio than urban population : <br>
```{r echo=FALSE}
#Make data frame
data = data.frame(fileObj$State,fileObj$Rural.Population,fileObj$Urban.Population)
#Print list of state which has less rural population then urban population 
```
```{r}
subset(data,fileObj.Rural.Population < fileObj.Urban.Population)
```

**1.B** Now calculate population of each state from top 500 cities only<br>
```{r echo = FALSE}
#Read from File
citys=read.csv("CSV/cities_r2.csv")

#Stroe name of states
states=unique(citys$state_name)
total=0
male=0
female=0
for (i in 1:length(states)) {
  total[i]=0
  male[i]=0
  female[i]=0
  for (j in 1:length(citys$state_name)) {
    if(identical(as.character(states[i]),as.character(citys$state_name[j]))){
      male[i]=male[i]+as.integer(citys$population_male[j])
      total[i]=total[i]+as.integer(citys$population_total[j])
      female[i]=female[i]+as.integer(citys$population_female[j])
    }
  }
}

#Convert to data Frames
data =data.frame(male,female,total,states)
#Draw graph
```
```{r }
hc <- highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(categories = data$states) %>% 
  hc_add_series(name = "Male", data = data$male) %>% 
  hc_add_series(name = "Female", data = data$female) %>% 
  hc_add_series(name = "Total", data = data$total) %>% 
  hc_title(text="Comparision of Male and Female Urban Population")
hc
```
Now some intersting fact from graph<br>
**Note** The below data is valid if we choose top 500 cities of India.<br>
(i) Maharashtra has maximum urban population.<br>
(ii) Maharashtra also has maximum male and female urban population.<br>
(iii) State who has more female population than male population.<br>
```{r}
subset(data,male < female)
```
**Union territory Puducherry** also has more female population then male population.<br>
(iv) State which do not have any top 500 cities<br>
(a)Meghalaya<br>
(b)Goa<br>
(c)Arunachal Pradesh<br>
(d)Sikkim<br>

**1.C** Top 10 City with highest Population
```{r}
#Read from file
Data = read.csv("~/Documents/R-Project/CSV/cities_r2.csv")
#Sort according to total population
data <- Data[with(Data,order(-population_total)),]
#find top 10 city
topCity = data[1:10,]
hc = hchart(topCity,"column",hcaes(x=name_of_city,y =population_total),name="total population",colorByPoint = TRUE) %>% hc_title(text = "Top 10 City by Total Population.") %>%
    hc_add_theme(hc_theme_monokai() )
hc
```
**1.D** Top 10 City with highest Male Population
```{r}
#Sort according to male population
data <- Data[with(Data,order(-population_male)),]
#find top 10 city
topCity = data[1:10,]
hc = hchart(topCity,"funnel",hcaes(x=name_of_city,y =population_male),name="male population",colorByPoint = TRUE) %>% hc_title(text = "Top 10 City by Male Population.")
hc
```
**1.E** Top 10 City with highest Female Population
```{r}
#Sort according to female population
data <- Data[with(Data,order(-population_female)),]
#find top 10 city
topCity = data[1:10,]
hc = hchart(topCity,"pyramid",hcaes(x=name_of_city,y =population_female),name="female population",colorByPoint = TRUE) %>% hc_title(text = "Top 10 City by female Population.")
hc
```
**1.F** Top 10 City with highest Child[0-6 age] Population
```{r}
#Sort according to 0-6 age population
data <- Data[with(Data,order(-X0.6_population_total)),]
#find top 10 city
topCity = data[1:10,]
hc = hchart(topCity,"pie",hcaes(x=name_of_city,y =X0.6_population_total),name="child[0-6 age] population",colorByPoint = TRUE) %>% hc_title(text = "Top 10 City by child Population.") 
hc
```
**1.G** Comparision of Top 10 City : 
```{r}
data <- Data[with(Data,order(-population_total)),]
topCity = data[1:10,]
hc <- highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(categories = topCity$name_of_city) %>% 
  hc_add_series(name = "Total population", data = topCity$population_total) %>% 
  hc_add_series(name = "Male population", data = topCity$population_male) %>% 
  hc_add_series(name = "Female population", data = topCity$population_female) %>% 
  hc_add_series(name = "Child population", data = topCity$X0.6_population_total) %>% 
  hc_title(text="Comparision of Top 10 City")
hc
```


## 2. Literacy Rate Analysis
**2.A** Indan State and Union territory by Literac rate
```{r echo =FALSE}
#Read from file
fileObj = read.csv("CSV/Literacy rate.csv")
#get data
states = fileObj$State
rate =  fileObj$Literacy_Rate_2011
#Convert to Data frame
data = data.frame(states,rate)
#Draw Graph
```
```{r}
hchart(data,"",hcaes(x=states,y = rate),name="Literacy rate 2011",colorByPoint = TRUE) %>% hc_title(text = "State and Union territory by Literacy rate 2011.")
```
**2.B**Comparison of Indan State and Union territory by Literac rate
```{r}
#Now draw graph using highcharter library
highchart() %>% 
  hc_xAxis(categories = fileObj$State ) %>% 
  hc_chart(type = "column") %>% 
  hc_add_series(name = "Total Literacy Rate", data = fileObj$Literacy_Rate_2011 ) %>% 
  hc_add_series(name = "Male Literacy Rate", data = fileObj$Male_Literacy_Rate_2011) %>% 
  hc_add_series(name = "Female Literacy Rate", data = fileObj$Female_Literacy_Rate_2011) %>% hc_title(text="Comparision of States and union terryterry by literacy rate.") 
```

Analysis from above graph <br>
(i) Kerala has Highest Litaracy Rate = 93.91 % <br>
(ii) Lakshadweep has Highest male literacy rate = 96.11% <br>
(iii) Kerala has Highest Female literacy rate = 91.98% <br>
(iv)Top 10 State according to difference between Male and Female Literacy rate <br>
```{r echo=FALSE}
#Read from File
Data = read.csv("CSV/Literacy rate.csv")
#Sort according to difference
data=Data[with(Data,order(-(Male_Literacy_Rate_2011 -Female_Literacy_Rate_2011 ))),]
#Select top 10
data = data[1:10,]
```
```{r}
#Draw graph
hchart(data,"column",hcaes(x=State,y = (Male_Literacy_Rate_2011 -Female_Literacy_Rate_2011 )),name="Difference B/w male and female Literacy rate 2011",colorByPoint = TRUE) %>%
  hc_title(text = "Top 10 State according to difference between Male and Female Literacy rate")
```

**2.C**Top 10 City by Literacy rate
```{r}
#Read from file
Data = read.csv("CSV/cities_r2.csv")
##Sort according to literacy rate
data <- Data[with(Data,order(-effective_literacy_rate_total)),]
#find top 10 city
topCity = data[1:10,]
highchart() %>% 
  hc_xAxis(categories = topCity$name_of_city ) %>% 
  hc_chart(type = "column") %>% 
  hc_add_series(name = "Total Literacy Rate", data = topCity$effective_literacy_rate_total ) %>% 
  hc_add_series(name = "Male Literacy Rate", data = topCity$effective_literacy_rate_male) %>% 
  hc_add_series(name = "Female Literacy Rate", data = topCity$effective_literacy_rate_female) %>% hc_title(text="Comparision of top 10 city by literacy rate.")
```
Analysis from Graph : <br>
(i) Aizawl(Mizoram) has highest Literacy rate = 98.80 <br>
(ii) Aizawl(Mizoram) has highest Male Literacy rate = 99.30 <br>
(iii) Aizawl(Mizoram) has highest Female Literacy rate =98.30 <br>



##3. Sex Ratio Analysis
**2.A** Indan State and Union territory by Sex ratio
```{r echo= FALSE}
#Read from file
fileObj = read.csv("CSV/SexRatio.csv")
#get data
states = fileObj$State
ratio =  fileObj$SexRatio
#Convert to Data frame
data = data.frame(states,ratio)
#Draw Graph
```
```{r}
hchart(data,"column",hcaes(x=states,y = ratio),name="Sex Ratio 2011",colorByPoint = TRUE) %>% 
  hc_title(text = "State and Union territory by Sex Ratio 2011.") %>%
  hc_add_theme(hc_theme_chalk())
```

(1) State having sex ratio more than 1000: <br>
  (a) Kerala 1084 <br>
  (b) Puducherry 1037 <br>
  
**3.B** Change in Sex ratio from 2001 to 2011
```{r echo = FALSE}
fileObj = read.csv("CSV/SexRatio.csv")
#get data
states = fileObj$State
change =  fileObj$Increase
#Convert to Data frame
data = data.frame(states,change)
```

```{r}
hchart(data,"column",hcaes(x=states,y = change),name="Sex Ratio 2011",colorByPoint = TRUE) %>% 
  hc_title(text = "State and Union territory by Change Percentage from 2001 to 2011.") %>%
  hc_add_theme(hc_theme_google())
```
(1). Sex ratio of Delhi Increased by 47 (maximum)<br>
(2). Sex ratio of Dadra and Nagar Haveli decreased by 38 <br>
(3). States whose Sex ratio Decreased : <br>
  (a)Bihar (-1)<br>
  (b)Gujarat (-1)<br>
  (c)Jammu and Kasmir (-3)<br>
  (4) Dadra and Nagar Haveli (-38)<br>


**3.C** Top 10 City according Sex ratio<br>
```{r}

#Read from file
Data = read.csv("~/Documents/R-Project/CSV/cities_r2.csv")
#Sort according to total population
data <- Data[with(Data,order(-sex_ratio)),]
#find top 10 city
topCity = data[1:10,]
hc = hchart(topCity,"pie",hcaes(x=name_of_city,y =sex_ratio),name="Sex ratio",colorByPoint = TRUE) %>% hc_title(text = "Top 10 City by Sex ratio.") %>%
  hc_add_theme(hc_theme_db())

hc
```


##4. Graduate Analysis

**4.A** Indian State by no of graduate
NOTE : Number of Graduate of state only from top 500 city.
```{r echo= FALSE}
#Read from File
citys=read.csv("CSV/cities_r2.csv")

#Stroe name of states
states=unique(citys$state_name)
total=0
male=0
female=0
for (i in 1:length(states)) {
  total[i]=0
  male[i]=0
  female[i]=0
  for (j in 1:length(citys$state_name)) {
    if(identical(as.character(states[i]),as.character(citys$state_name[j]))){
      male[i]=male[i]+as.integer(citys$male_graduates[j])
      total[i]=total[i]+as.integer(citys$total_graduates[j])
      female[i]=female[i]+as.integer(citys$female_graduates[j])
    }
  }
}

data =data.frame(male,female,total,states)

```

```{r}

hc <- highchart() %>% 
  hc_chart(type = "bar") %>% 
  hc_xAxis(categories = data$states) %>% 
  hc_add_series(name = "Total", data = data$total) %>% 
  hc_title(text="State by Number of Graduate in 2015-16") %>%
  hc_add_theme(hc_theme_handdrawn() )
hc
```

**4.B** State by Umemployment Rate : 

```{r echo = FALSE}
fileObj = read.csv("CSV/Unemp.csv")
#get data
states = fileObj$State
total =  fileObj$Total
#Convert to Data frame
data = data.frame(states,total)
```

```{r}
hchart(data,"pyramid",hcaes(x=states,y = total),name="Unemployment rate : ",colorByPoint = TRUE) %>% 
  hc_title(text = "Unemployment Rate of each state.") %>%
  hc_add_theme(hc_theme_gridlight() )
```

(1) Gujarat has lowest unemployment rate in India(9)
(2) Tripura has highest unemployment rate in India(197)

<h1>  Thank You </h1>


